Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-17 paper.tex
add references to figshare tarball of code, data, etc.

These characteristics result in a fleet reactor having perfect fuel sharing
and perfect cycle staggering among the individual reactors it models.  First
discharge of spent fuel from fleets begins immediately rather than after a
complete refueling cycle. Fuel shortages also only cause proportional loss of
capacity rather than whole-reactor quantized shutdown.

@@

The input files and other assets used in the analysis for each of the four
cases can be found in TODO: cite figshare tarball.

@@

>>>>

These characteristics result in a fleet reactor having perfect fuel sharing
and perfect cycle staggering among the individual reactors it models.  First
discharge of spent fuel from fleets begins immediately rather than after a
complete refueling cycle. Fuel shortages also only cause proportional loss of
capacity rather than whole-reactor quantized shutdown.  The full
implementation of the fleet-based reactor is publicy available for download
\cite{Carlsen2015}.

@@

The input files and other assets used in the analysis for each of the four
cases are publicly available for download \cite{Carlsen2015}.

@@

All results data, analysis tools and instructions are publicly available for
download at \url{http://dx.doi.org/10.6084/m9.figshare.1546775}
\cite{Carlsen2015}.
